---
title: "Compute Global Max Similarity Matrix for 2 Sequences"
author: "Conor Heffron"
date: "2024-07-14"
output: github_document
---

# Objective: Compute the global max similarity matrix between the two sequences:
- AAGTGCCTCAAGATA
- ACCGTCTCAGCAATA

## Load scripts & libraries
```{r}
library(stringr)
source('../R/global-max-sim-matrix.R')
```

## Define Sequence 1
```{r}
seq1 <- 'AAGTGCCTCAAGATA'
seq1
```
## Define Sequence 2
```{r}
seq2 <- 'ACCGTCTCAGCAATA'
seq2
```

## Get Sequence 1 & 2 Lengths
```{r}
m <- nchar(seq1)
n <- nchar(seq2)
print(paste('Sequence Length (seq1, seq2):', m, n))
```

## Create Initial Matrix Object & fill with Zeros
```{r}
# Construct default similarity matrix and fill with 0's
sim_matrix <- matrix(0, m+1, n+1)
sim_matrix
```
## Compute First Column Values
```{r}
sim_matrix <- init_matrix_col1(sim_matrix, m)
sim_matrix
```

## Compute First Row Values
```{r}
sim_matrix <- init_matrix_row1(sim_matrix, n)
sim_matrix
```

```{r}
# define score look-up map
d <- c("match" = 1, "mismatch" = -1, "gap" = -2)
d
```

## Compute Global Max Similarity Matrix for seq1 & seq2
```{r}
sim_matrix <- populate_global_max_sim_matrix(sim_matrix, seq1, seq2, d, m, n)
sim_matrix
```
## Label columns and rows
```{r}
# colnames(sim_matrix) <- c('-', 'A', 'A', 'G', 'T', 'G', 'C', 'C', 'T', 'C', 'A', 'A', 'G', 'A', 'T', 'A')
colnames(sim_matrix) <- unlist(stringr::str_split(paste('-', seq1, sep=''), boundary("character")))

# rownames(sim_matrix) <- c('-', 'A', 'C', 'C', 'G', 'T', 'C', 'T', 'C', 'A', 'G', 'C', 'A', 'A', 'T', 'A')
rownames(sim_matrix) <- unlist(stringr::str_split(paste('-', seq2, sep=''), boundary("character")))
```

## Final Matrix Output
```{r}
sim_matrix
```
